Coinfluence: The Role of Currency Numerosity in Consumer Decision Making

### 2024-12-21 paper.tex
feat: update paper to final version

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Coinfluence: The Role of Currency Numerosity in Consumer Decision Making},
  pdflang={en-GB},
  pdfkeywords={Behavioural Economics, Face Value Effect, Consumer Choice
Theory},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

  \author{1054398}
            \affil{%
                  University of Oxford
              }

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Coinfluence: The Role of Currency Numerosity in Consumer Decision Making},
  pdfauthor={Konrad Kopp},
  pdflang={en-GB},
  pdfkeywords={Behavioural Economics, Face Value Effect, Consumer Choice
Theory},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

  \author{Konrad Kopp}
            \affil{%
                  University of Oxford
              }
